Temperature and moisture effects on greenhouse gas emissions from deep active-layer boreal soils

### 2016-04-25 manuscript/cpcrw_manuscript.Rmd
Fixed figure 3 warning, and more tweaks to pclean

pclean <- function(x, digits = 3, printP = TRUE) {  # pretty formatting of p-values
  ltstring <- paste0("< 0.", substr("000000000", 1, digits - 1), "1")
  valstring <- ifelse(x < 10^-digits, ltstring, formatC(x, digits = digits, format = 'f'))
  if(printP) {
    ifelse(x < 0.001, valstring, paste("=", valstring)) %>% paste("P", .)
  } else {
    valstring
  }
}

@@

>>>>

@@

# 'Clean p value' function to pretty-print p value(s), specifically
pclean <- function(x, digits = 3, printP = TRUE) {
  ltstring <- paste0("< 0.", paste(rep("0", digits - 1), collapse = ""), "1")
  valstring <- ifelse(x < 10^-digits, ltstring, pn(x, digits))
  if(printP) {
    ifelse(x < 10^-digits, valstring, paste("=", valstring)) %>% paste("P", .)
  } else {
    valstring
  }
}
